### 2021-03-13 README.Rmd
addy mcaddadd

That will direct you here. Scroll down your available project types until you see my "Steve project" entry. It will have that "S" icon (that is incidentally the icon for my website). Select it.

>>>>

That will direct you here. Scroll down your available project types until you see my "S" icon, which is incidentally the favicon on [my website](http://svmiller.com). Select that entry to create a new academic paper/project.
